---
title: 'Modelling age'
output:
  html_document:
    code_folding: hide
    highlight: tango
    theme: united
    toc: yes
    toc_depth: 4
    toc_float: yes
editor_options:
  chunk_output_type: console
---

```{r options, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE, comment = FALSE,
  cache.lazy = FALSE
)
options(scipen = 999)
options(knitr.kable.NA = "")
```

```{r packages, include=FALSE}
# packages -----
library(kableExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rms)
library(stargazer)
library(ggstance)
library(stringr)
library(knitr)
```

```{r data, include=FALSE}
setwd("M:/Elena - R/Multi-state  cancer")
load("1 data prep/working.data.Rda")
```

```{r functions}
## Functions

# For printing numbers
nice.num <- function(x) {
  prettyNum(x, big.mark = ",", nsmall = 0, digits = 0, scientific = FALSE)
}
nice.num2 <- function(x) {
  prettyNum(x, big.mark = ",", nsmall = 2, digits = 2, scientific = FALSE)
}

# Models
get.models <- function(r.data, name) {
  # will add models to list-----
  models <- list()


  ## overall models ------
  # data
  working.data <- r.data
  dd <<- datadist(working.data)
  options(datadist = "dd")


  # minimally adjusted -age, gender, cancer
  models[[paste0("m.", name, ".overall.linear", "age.min.adjusted")]] <- cph(Surv(time, status) ~ age +
    gender + cancer,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.quadratic", "age.min.adjusted")]] <- cph(Surv(time, status) ~
  pol(age, 2) +
    gender + cancer,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.rcs3", "age.min.adjusted")]] <- cph(Surv(time, status) ~
  rcs(age, 3) +
    gender + cancer,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.rcs4", "age.min.adjusted")]] <- cph(Surv(time, status) ~
  rcs(age, 4) +
    gender + cancer,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.rcs5", "age.min.adjusted")]] <- cph(Surv(time, status) ~
  rcs(age, 5) + gender + cancer,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  ###########
  # medium adjustment - `smoke and medea
  models[[paste0("m.", name, ".overall.linear", ".age.med.adjusted")]] <- cph(Surv(time, status) ~
  age +
    cancer + gender + medea + smoke.all_time,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )
  models[[paste0("m.", name, ".overall.quadratic", ".age.med.adjusted")]] <- cph(Surv(time, status) ~
  pol(age, 2) +
    cancer + gender + medea + smoke.all_time,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.rcs3", ".age.med.adjusted")]] <- cph(Surv(time, status) ~
  rcs(age, 3) +
    cancer + gender + medea + smoke.all_time,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.rcs4", ".age.med.adjusted")]] <- cph(Surv(time, status) ~
  rcs(age, 4) +
    cancer + gender + medea + smoke.all_time,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.rcs5", ".age.med.adjusted")]] <- cph(Surv(time, status) ~
  rcs(age, 5) +
    cancer + gender + medea + smoke.all_time,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  # fully adjusted - + comorbidities
  models[[paste0("m.", name, ".overall.linear", ".age.fully.adjusted")]] <- cph(Surv(time, status) ~
  age +
    cancer + gender + medea + smoke.all_time +
    a_autoimmune_condition + a_chronic_kidney_disease + a_copd +
    a_dementia + a_heart_disease + a_hyperlipidemia +
    a_hypertension + a_t2_diabetes + a_obesity,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.quadratic", ".age.fully.adjusted")]] <- cph(Surv(time, status) ~
  pol(age, 2) +
    cancer + gender + medea + smoke.all_time +
    a_autoimmune_condition + a_chronic_kidney_disease + a_copd +
    a_dementia + a_heart_disease + a_hyperlipidemia +
    a_hypertension + a_t2_diabetes + a_obesity,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.rcs3", ".age.fully.adjusted")]] <- cph(Surv(time, status) ~
  rcs(age, 3) +
    cancer + gender + medea + smoke.all_time +
    a_autoimmune_condition + a_chronic_kidney_disease + a_copd +
    a_dementia + a_heart_disease + a_hyperlipidemia +
    a_hypertension + a_t2_diabetes + a_obesity,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.rcs4", ".age.fully.adjusted")]] <- cph(Surv(time, status) ~
  rcs(age, 4) +
    cancer + gender + medea + smoke.all_time +
    a_autoimmune_condition + a_chronic_kidney_disease + a_copd +
    a_dementia + a_heart_disease + a_hyperlipidemia +
    a_hypertension + a_t2_diabetes + a_obesity,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )

  models[[paste0("m.", name, ".overall.rcs5", ".age.fully.adjusted")]] <- cph(Surv(time, status) ~
  rcs(age, 5) +
    cancer + gender + medea + smoke.all_time +
    a_autoimmune_condition + a_chronic_kidney_disease + a_copd +
    a_dementia + a_heart_disease + a_hyperlipidemia +
    a_hypertension + a_t2_diabetes + a_obesity,
  surv = TRUE, x = TRUE, y = TRUE,
  data = working.data, iter.max = 200
  )


  ## output ----
  models
}


# To get relative hazards for each model in list
# also add in AIC and BIC
get.r.hazard <- function(models, # list of models
                         age.1, # reference age
                         age.2) { # comparison ages


  output <- lapply(models, function(x) {
    model <- x
    output <- NULL
    for (i in 1:length(age.2)) {
      working.summary <- head(as.data.frame(summary({{ model }},
        age = c({{ age.1 }}, {{ age.2[i] }}), antilog = FALSE
      )), 1) # 1st- age
      working.summary <- working.summary %>%
        select(Effect, `Lower 0.95`, `Upper 0.95`) %>%
        mutate(
          hr = exp(Effect),
          hr.low = exp(`Lower 0.95`),
          hr.high = exp(`Upper 0.95`)
        ) %>%
        mutate(
          ref.age = age.1,
          rel.age = age.2[i]
        ) %>%
        select(hr, hr.low, hr.high, ref.age, rel.age)
      # browser()
      working.summary$aic <- AIC({{ model }})
      working.summary$bic <- BIC({{ model }})

      output <- rbind(output, working.summary)
    }

    output
  })
  # to dataframe
  output <- bind_rows(output, .id = "model")
  output
}
```

```{r, cache=TRUE}
# get models -----
models.healthy.diagnosis <- get.models(
  r.data = r.healthy.diagnosis,
  name = "healthy.diagnosis"
)

models.healthy.hospitalised <- get.models(
  r.data = r.healthy.hospitalised,
  name = "healthy.hospitalised"
)

models.healthy.death <- get.models(
  r.data = r.healthy.death,
  name = "healthy.death"
)

models.diagnosis.hospitalised <- get.models(
  r.data = r.diagnosis.hospitalised,
  name = "diagnosis.hospitalised"
)

models.diagnosis.death <- get.models(
  r.data = r.diagnosis.death,
  name = "diagnosis.death"
)

models.hospitalised.death <- get.models(
  r.data = r.hospitalised.death,
  name = "hospitalised.death"
)
```

# Transition: From general population to diagnosed with COVID-19 - 

```{r}
# models and relative hazards from models -----
r.hazard <- get.r.hazard(
  model = models.healthy.diagnosis,
  age.1 = 65,
  age.2 = seq(0, 100, 1)
)
```

## Comparison of alternative models
### Model fit - selected model: all 5 splines

```{r}
fit <- rbind(
  # overall - age only
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.min.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.min.adjusted"),

  # overall - mid ajusted

  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.med.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.med.adjusted"),

  # overall - fully.adjusted
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, "age.fully.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.fully.adjusted")
)

fit <- fit %>%
  pivot_wider(
    names_from = name,
    values_from = c(aic, bic)
  )
```

```{r}


fit <- fit %>%
  select(
    type,
    aic_overall.age.min.adjusted, bic_overall.age.min.adjusted,
    aic_overall.age.med.adjusted, bic_overall.age.med.adjusted,
    aic_overall.fully.adjusted, bic_overall.fully.adjusted
  )

fit <- fit %>%
  mutate_at(2:ncol(fit), funs(as.numeric(str_replace_all(., ",", ""))))

for (i in 2:ncol(fit)) {
  val.min <- min(fit[, i])
  fit <- fit %>% mutate_at(i, funs(ifelse(. == val.min, cell_spec(., background = "orange"), .)))
}
fit <- fit %>% mutate_at(2:ncol(fit), funs(nice.num(.)))


kable(
  escape = F, fit %>%
    mutate(type = ifelse(type == "rcs3",
      "restricted cubic spline (3 knots)",
      ifelse(type == "rcs4",
        "restricted cubic spline (4 knots)",
        ifelse(type == "rcs5",
          "restricted cubic spline (5 knots)",
          type
        )
      )
    )),
  col.names = c(
    "Type",
    "AIC", "BIC",
    "AIC", "BIC",
    "AIC", "BIC"
  )
) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>%
  add_header_above(c("",
    "Overall - min adjusted" = 2,
    "Overall - med adjusted" = 2,
    "Overall - fully adjusted" = 2
  )) %>%
  add_header_above(
    c("Fit from alternative appoaches to modelling age" = 7)
  ) %>%
  add_header_above(
    c("From general population to diagnosed with COVID-19" = 7)
  )
```

# Transition: From healthy to hospitalised 
```{r}
# models and relative hazards from models -----
r.hazard <- get.r.hazard(
  model = models.healthy.hospitalised,
  age.1 = 65,
  age.2 = seq(0, 100, 1)
)
```

## Comparison of alternative models
### Model fit - - selected modell: all quadratic

```{r}
fit <- rbind(
  # overall - age only
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.min.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.min.adjusted"),

  # overall - mid ajusted

  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.med.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.med.adjusted"),

  # overall - fully.adjusted
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, "age.fully.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.fully.adjusted")
)

fit <- fit %>%
  pivot_wider(
    names_from = name,
    values_from = c(aic, bic)
  )
```

```{r}


fit <- fit %>%
  select(
    type,
    aic_overall.age.min.adjusted, bic_overall.age.min.adjusted,
    aic_overall.age.med.adjusted, bic_overall.age.med.adjusted,
    aic_overall.fully.adjusted, bic_overall.fully.adjusted
  )

fit <- fit %>%
  mutate_at(2:ncol(fit), funs(as.numeric(str_replace_all(., ",", ""))))

for (i in 2:ncol(fit)) {
  val.min <- min(fit[, i])
  fit <- fit %>% mutate_at(i, funs(ifelse(. == val.min, cell_spec(., background = "orange"), .)))
}
fit <- fit %>% mutate_at(2:ncol(fit), funs(nice.num(.)))


kable(
  escape = F, fit %>%
    mutate(type = ifelse(type == "rcs3",
      "restricted cubic spline (3 knots)",
      ifelse(type == "rcs4",
        "restricted cubic spline (4 knots)",
        ifelse(type == "rcs5",
          "restricted cubic spline (5 knots)",
          type
        )
      )
    )),
  col.names = c(
    "Type",
    "AIC", "BIC",
    "AIC", "BIC",
    "AIC", "BIC"
  )
) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>%
  add_header_above(c("",
    "Overall - min adjusted" = 2,
    "Overall - med adjusted" = 2,
    "Overall - fully adjusted" = 2
  )) %>%
  add_header_above(
    c("Fit from alternative appoaches to modelling age" = 7)
  ) %>%
  add_header_above(
    c("From general population to hospitalised with COVID-19" = 7)
  )
```



# Transition: From Diagnosed to Hospitalised 
```{r}
# models and relative hazards from models -----
r.hazard <- get.r.hazard(
  model = models.diagnosis.hospitalised,
  age.1 = 65,
  age.2 = seq(0, 100, 1)
)
```

## Comparison of alternative models
### Model fit - selected model: all 5 splines 

```{r}
fit <- rbind(
  # overall - age only
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.min.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.min.adjusted"),

  # overall - mid ajusted

  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.med.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.med.adjusted"),

  # overall - fully.adjusted
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, "age.fully.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.fully.adjusted")
)

fit <- fit %>%
  pivot_wider(
    names_from = name,
    values_from = c(aic, bic)
  )
```

```{r}


fit <- fit %>%
  select(
    type,
    aic_overall.age.min.adjusted, bic_overall.age.min.adjusted,
    aic_overall.age.med.adjusted, bic_overall.age.med.adjusted,
    aic_overall.fully.adjusted, bic_overall.fully.adjusted
  )

fit <- fit %>%
  mutate_at(2:ncol(fit), funs(as.numeric(str_replace_all(., ",", ""))))

for (i in 2:ncol(fit)) {
  val.min <- min(fit[, i])
  fit <- fit %>% mutate_at(i, funs(ifelse(. == val.min, cell_spec(., background = "orange"), .)))
}
fit <- fit %>% mutate_at(2:ncol(fit), funs(nice.num(.)))


kable(
  escape = F, fit %>%
    mutate(type = ifelse(type == "rcs3",
      "restricted cubic spline (3 knots)",
      ifelse(type == "rcs4",
        "restricted cubic spline (4 knots)",
        ifelse(type == "rcs5",
          "restricted cubic spline (5 knots)",
          type
        )
      )
    )),
  col.names = c(
    "Type",
    "AIC", "BIC",
    "AIC", "BIC",
    "AIC", "BIC"
  )
) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>%
  add_header_above(c("",
    "Overall - min adjusted" = 2,
    "Overall - med adjusted" = 2,
    "Overall - fully adjusted" = 2
  )) %>%
  add_header_above(
    c("Fit from alternative appoaches to modelling age" = 7)
  ) %>%
  add_header_above(
    c("From diagnosed with COVID-19 to hospitalised with COVID-19" = 7)
  )
```

# Transition: From diagnosed to death
```{r}
# models and relative hazards from models -----
r.hazard <- get.r.hazard(
  model = models.diagnosis.death,
  age.1 = 65,
  age.2 = seq(0, 100, 1)
)
```

## Comparison of alternative models
### Model fit - selected model all quadratic

```{r}
fit <- rbind(
  # overall - age only
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.min.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.min.adjusted"),

  # overall - mid ajusted

  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.med.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.med.adjusted"),

  # overall - fully.adjusted
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, "age.fully.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.fully.adjusted")
)

fit <- fit %>%
  pivot_wider(
    names_from = name,
    values_from = c(aic, bic)
  )
```

```{r}
fit <- fit %>%
  select(
    type,
    aic_overall.age.min.adjusted, bic_overall.age.min.adjusted,
    aic_overall.age.med.adjusted, bic_overall.age.med.adjusted,
    aic_overall.fully.adjusted, bic_overall.fully.adjusted
  )

fit <- fit %>%
  mutate_at(2:ncol(fit), funs(as.numeric(str_replace_all(., ",", ""))))

for (i in 2:ncol(fit)) {
  val.min <- min(fit[, i])
  fit <- fit %>% mutate_at(i, funs(ifelse(. == val.min, cell_spec(., background = "orange"), .)))
}
fit <- fit %>% mutate_at(2:ncol(fit), funs(nice.num(.)))


kable(
  escape = F, fit %>%
    mutate(type = ifelse(type == "rcs3",
      "restricted cubic spline (3 knots)",
      ifelse(type == "rcs4",
        "restricted cubic spline (4 knots)",
        ifelse(type == "rcs5",
          "restricted cubic spline (5 knots)",
          type
        )
      )
    )),
  col.names = c(
    "Type",
    "AIC", "BIC",
    "AIC", "BIC",
    "AIC", "BIC"
  )
) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>%
  add_header_above(c("",
    "Overall - min adjusted" = 2,
    "Overall - med adjusted" = 2,
    "Overall - fully adjusted" = 2
  )) %>%
  add_header_above(
    c("Fit from alternative appoaches to modelling age" = 7)
  ) %>%
  add_header_above(
    c("From diagnosed with COVID-19 to death" = 7)
  )
```


# Transition: From hospitalised to death 
```{r}
# models and relative hazards from models -----
r.hazard <- get.r.hazard(
  model = models.hospitalised.death,
  age.1 = 65,
  age.2 = seq(0, 100, 1)
)
```

## Comparison of alternative models
### Model fit - selected model:Min adjusted, linear / others: 3 splines

```{r}
fit <- rbind(
  # overall - age only
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.min.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.min.adjusted"),

  # overall - mid ajusted

  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.med.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.med.adjusted"),

  # overall - fully.adjusted
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, "age.fully.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.fully.adjusted")
)

fit <- fit %>%
  pivot_wider(
    names_from = name,
    values_from = c(aic, bic)
  )
```

```{r}
fit <- fit %>%
  select(
    type,
    aic_overall.age.min.adjusted, bic_overall.age.min.adjusted,
    aic_overall.age.med.adjusted, bic_overall.age.med.adjusted,
    aic_overall.fully.adjusted, bic_overall.fully.adjusted
  )

fit <- fit %>%
  mutate_at(2:ncol(fit), funs(as.numeric(str_replace_all(., ",", ""))))

for (i in 2:ncol(fit)) {
  val.min <- min(fit[, i])
  fit <- fit %>% mutate_at(i, funs(ifelse(. == val.min, cell_spec(., background = "orange"), .)))
}
fit <- fit %>% mutate_at(2:ncol(fit), funs(nice.num(.)))


kable(
  escape = F, fit %>%
    mutate(type = ifelse(type == "rcs3",
      "restricted cubic spline (3 knots)",
      ifelse(type == "rcs4",
        "restricted cubic spline (4 knots)",
        ifelse(type == "rcs5",
          "restricted cubic spline (5 knots)",
          type
        )
      )
    )),
  col.names = c(
    "Type",
    "AIC", "BIC",
    "AIC", "BIC",
    "AIC", "BIC"
  )
) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>%
  add_header_above(c("",
    "Overall - min adjusted" = 2,
    "Overall - med adjusted" = 2,
    "Overall - fully adjusted" = 2
  )) %>%
  add_header_above(
    c("Fit from alternative appoaches to modelling age" = 7)
  ) %>%
  add_header_above(
    c("From hospitalised with COVID-19 to death" = 7)
  )
```

# Transition: From healthy to death 

```{r}
# models and relative hazards from models -----
r.hazard <- get.r.hazard(
  model = models.healthy.death,
  age.1 = 65,
  age.2 = seq(0, 100, 1)
)
```

## Comparison of alternative models
### Model fit - selected model: all 5 splines

```{r}
fit <- rbind(
  # overall - age only
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.min.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.min.adjusted"),

  # overall - mid ajusted

  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, ".age.med.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.age.med.adjusted"),

  # overall - fully.adjusted
  r.hazard %>%
    filter(str_detect(model, ".overall")) %>%
    filter(str_detect(model, "age.fully.adjusted")) %>%
    select(model, aic, bic) %>%
    distinct() %>%
    mutate(bic = nice.num(bic)) %>%
    mutate(aic = nice.num(aic)) %>%
    mutate(type = str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse = "|"))) %>%
    select(type, aic, bic) %>%
    mutate(name = "overall.fully.adjusted")
)

fit <- fit %>%
  pivot_wider(
    names_from = name,
    values_from = c(aic, bic)
  )
```

```{r}


fit <- fit %>%
  select(
    type,
    aic_overall.age.min.adjusted, bic_overall.age.min.adjusted,
    aic_overall.age.med.adjusted, bic_overall.age.med.adjusted,
    aic_overall.fully.adjusted, bic_overall.fully.adjusted
  )

fit <- fit %>%
  mutate_at(2:ncol(fit), funs(as.numeric(str_replace_all(., ",", ""))))

for (i in 2:ncol(fit)) {
  val.min <- min(fit[, i])
  fit <- fit %>% mutate_at(i, funs(ifelse(. == val.min, cell_spec(., background = "orange"), .)))
}
fit <- fit %>% mutate_at(2:ncol(fit), funs(nice.num(.)))


kable(
  escape = F, fit %>%
    mutate(type = ifelse(type == "rcs3",
      "restricted cubic spline (3 knots)",
      ifelse(type == "rcs4",
        "restricted cubic spline (4 knots)",
        ifelse(type == "rcs5",
          "restricted cubic spline (5 knots)",
          type
        )
      )
    )),
  col.names = c(
    "Type",
    "AIC", "BIC",
    "AIC", "BIC",
    "AIC", "BIC"
  )
) %>%
  kable_styling(bootstrap_options = c("striped", "bordered")) %>%
  add_header_above(c("",
    "Overall - min adjusted" = 2,
    "Overall - med adjusted" = 2,
    "Overall - fully adjusted" = 2
  )) %>%
  add_header_above(
    c("Fit from alternative appoaches to modelling age" = 7)
  ) %>%
  add_header_above(
    c("From general population to death" = 7)
  )
```
